### 2020-02-21 README.Rmd
update README

```{r}
vostok_co2 <- system.file("extdata", "vostok.icecore.co2", package = "contenturi")
readLines(vostok_co2, n = 25)
```

@@

```{r}
co2_url <- "http://cdiac.ornl.gov/ftp/trends/co2/vostok.icecore.co2"
register(co2_url)
```

@@

```{r}
lookup("hash://sha256/9412325831dab22aeebdd674b6eb53ba6b7bdd04bb99a4dbb21ddff646287e37")
```

@@

>>>>

```{r}
vostok_co2 <- system.file("extdata", "vostok.icecore.co2", package = "contenturi")
readLines(vostok_co2, n = 10)
```

@@

```{r}
# Oh no, the official version is 503 errors.  Lets use this backup
co2_url <- "https://github.com/espm-157/climate-template/releases/download/data/vostok.icecore.co2"
register(co2_url)
```

@@

```{r}
query("hash://sha256/9412325831dab22aeebdd674b6eb53ba6b7bdd04bb99a4dbb21ddff646287e37")
```

@@

## Local Registries & Local Storage

We can also store and register content locally following this same scheme.

```{r}
store(co2_url)
```

Now when we query for the hash, we see a local storage location as well:

```{r}
query("hash://sha256/9412325831dab22aeebdd674b6eb53ba6b7bdd04bb99a4dbb21ddff646287e37")
```

The `retreive()` verb (subject to change), provides a wrapper around `query` that always returns exactly one local path to requested content.  It will check for a stored copy of the content first, and download (and verify) remote content otherwise:

```{r}
path <- retrieve("hash://sha256/9412325831dab22aeebdd674b6eb53ba6b7bdd04bb99a4dbb21ddff646287e37")
```

Let's take a peak at the returned copy:

```{r}
readLines(path, n = 10)
## we could manually verify identity, though retrieve has already done this:

content_uri(path)
```
